acquisition of TEs

### 2021-06-03 Analyze_TEs.Rmd
updated analysis

# Correlation among variables in the observed data
```{r}
Correlation <- keepers_ws_TE %>%
  select(age_continuous, Average_90percentile, balance_vocab, word_vocab, TotalNW_Dom, TotalNW_NonDom,
         number_of_te, Dom_unique_words, NonDom_unique_words, concept_vocab) %>%
  # rename variables
  rename(Age_month = age_continuous,
         V = Average_90percentile,
         B = balance_vocab, 
         W = word_vocab,
         D = TotalNW_Dom, 
         N = TotalNW_NonDom, 
         TE = number_of_te, 
         DI = Dom_unique_words, 
         NI = NonDom_unique_words, 
         C = concept_vocab)

>>>>

# Correlation among variables in the observed data
```{r}
Correlation <- keepers_ws_TE %>%
  select(age_continuous, Average_90percentile, balance_vocab, word_vocab, TotalNW_Dom, TotalNW_NonDom,
         number_of_te, Dom_unique_words, NonDom_unique_words, concept_vocab) %>%
  # rename variables
  rename(Age_month = age_continuous,
         LEARNABLE = Average_90percentile,
         BALANCE = balance_vocab, 
         WORD = word_vocab,
         DOM = TotalNW_Dom, 
         NONDOM = TotalNW_NonDom, 
         TE = number_of_te, 
         "DOM-SINGLET" = Dom_unique_words, 
         "NONDOM-SINGLET" = NonDom_unique_words, 
         CONCEPT = concept_vocab)
